A Spiking Independent Accumulator Model for Winner-Take-All

### 2017-01-26 doc/paper/paper.tex
Update figures and captions.

\section{Results}
We find that the ability to form a clear decision of the LCA network decreases with more noise and less target separation  (see Fig.~\ref{fig:decisions}).
Also, the magnitude of the inputs has an important influence.
For a small inputs with $u=0.2$ the winner will mostly not exceed the 0.15 threshold with noise present.
The best performance is achieved with medium inputs with $u=0.6$.
Higher inputs make it more likely that runner-ups will exceed the 0.15 threshold, especially with a small target separation.
In contrast to the LCA network, the IA network manages to form a clear decision in every trial (not explicitly shown in Figure~\ref{fig:decisions}, but all data points would fall on the grey line).
\begin{figure*}[t]
    \centering
    \includegraphics{figures/decisions}
    \caption{
        Fraction of trials with a clear decision for different input noise standard deviations $\sigma$, target separations $s$, and input baselines $u$ for the LCA network.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line shows the optimum.
        It coincides with the performance of the IA network.
    }\label{fig:decisions}
\end{figure*}

Interestingly, for all successful decisions the correct winner was determined by the LCA network.
Thus, a plot of correct trials looks virtually identical to Figure~\ref{fig:decisions}.
While always reaching a decision, the decisions of the IA network are not always correct.
Overall, the IA performance tends to be worse for a high input magnitude, but better for smaller inputs (Fig.~\ref{fig:correct}a,\,b).
We can greatly improve the IA performance by increasing $\tau_1$ to \SI{0.5}{\second} which slows down the integration of evidence (Fig.~\ref{fig:correct}c).
This improves the IA performance to be above the LCA performance for high baselines, but it will also increase the decisions times of the IA network.
For a low baseline with $u=0.2$, it makes the IA network unable to decide within the allocated time frame, but given more time it would still reach a decision.
%A further improvement to the IA network is possible by eliminating a systematic bias introduced in the second layer of the IA network.
%In the NEF the neuron gain and bias parameters are usually picked from random distributions.
%As such the layer 2 populations will become active at slightly different thresholds.
%By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
\begin{figure*}[t]
    \centering
    \includegraphics{figures/correct}
    \caption{
        Fraction of correct trials for different input noise standard deviations $\sigma$, target separations $s$, and models.  
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line shows the optimum.
    }\label{fig:correct}
\end{figure*}

The time required to reach a decision in the LCA network depends mostly on the size of inputs and target separation (see Fig.~\ref{fig:time}a).
The level of noise only had a minor influence and was averaged over.
In the IA network the strongest input is the most important factor (dashed vs. solid lines in Fig.~\ref{fig:time}b).
Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time with a $\tau_1$ that achieves the same fraction of correct responses.
There is also a slight influence of target separation and input noise with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
\begin{figure*}[t]
    \centering
    \includegraphics{figures/time}
    \caption{
        (a) Mean decision times for different baselines $u$ and target separations $s$ for the LCA.
        (b) For the IA network $u = 0.2$ (solid) and $u = 1.0$ (dashed) are shown for different noise standard deviations $s$ and target separations $s$.
        Error bars denote bootstrapped 95\% confidence intervals.
    }\label{fig:time}
\end{figure*}

Finally, looking at the transient responses both models might produce outputs of losing choices.
For the LCA network the magnitude of the transient response mainly increases with the amount of noise (Fig.~\ref{fig:transient}a).
For the IA network, transient outputs are smaller in noisy conditions, but can be higher than for the LCA network in less noisy conditions with small target separations.
The magnitude of such transient responses is reduced by adjusting $\tau_1$ to 0.5.
\begin{figure*}
    \centering
    \includegraphics{figures/transient}
    \caption{
        Highest output of losing choices for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal lines show the optimum.
    }\label{fig:transient}
\end{figure*}

>>>>

\section{Results}
We find that the ability to form a clear decision of the LCA network decreases with more noise and less target separation  (see Fig.~\ref{fig:decisions}).
Also, the magnitude of the inputs has an important influence.
For a small inputs with $u=0.2$ the winner will mostly not exceed the 0.15 threshold with noise present.
The best performance is achieved with medium inputs with $u=0.6$.
Higher inputs make it more likely that runner-ups will exceed the 0.15 threshold, especially with a small target separation.
In contrast to the LCA network, the IA network manages to form a clear decision in every trial (not explicitly shown in Figure~\ref{fig:decisions}, but all data points would fall on the grey line).
\begin{figure*}[t]
    \centering
    \includegraphics{figures/decisions}
    \caption{
        Fraction of trials with a clear decision for the LCA network.
        Each plot shows data for a different input magnitude $u$.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line shows the optimum.
        It coincides with the performance of the IA network.
    }\label{fig:decisions}
\end{figure*}

Interestingly, for all successful decisions the correct winner was determined by the LCA network.
Thus, a plot of correct trials looks virtually identical to Figure~\ref{fig:decisions}.
While always reaching a decision, the decisions of the IA network are not always correct.
Overall, the IA performance tends to be worse for a high input magnitude, but better for smaller inputs (Fig.~\ref{fig:correct}a,\,b).
We can greatly improve the IA performance by increasing $\tau_1$ to \SI{0.5}{\second} which slows down the integration of evidence (Fig.~\ref{fig:correct}c).
This improves the IA performance to be above the LCA performance for high baselines, but it will also increase the decisions times of the IA network.
For a low baseline with $u=0.2$, it makes the IA network unable to decide within the allocated time frame, but given more time it would still reach a decision.
%A further improvement to the IA network is possible by eliminating a systematic bias introduced in the second layer of the IA network.
%In the NEF the neuron gain and bias parameters are usually picked from random distributions.
%As such the layer 2 populations will become active at slightly different thresholds.
%By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
\begin{figure*}[t]
    \centering
    \includegraphics{figures/correct}
    \caption{
        Fraction of correct trials for the IA network.  
        Each plot shows data for a different combination of input magnitude $u$ and integration time constant $\tau_1$.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line shows the optimum.
    }\label{fig:correct}
\end{figure*}

The time required to reach a decision in the LCA network depends mostly on the size of inputs and target separation (see Fig.~\ref{fig:time}a).
The level of noise only had a minor influence and was averaged over.
In the IA network the strongest input is the most important factor (dashed vs. solid lines in Fig.~\ref{fig:time}b).
Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time with a $\tau_1$ that achieves the same fraction of correct responses.
There is also a slight influence of target separation and input noise with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
\begin{figure*}[t]
    \centering
    \includegraphics{figures/time}
    \caption{
        Left: mean decision times for the LCA network. Shown data is averaged over all noise levels as it only had minor influence on the decision times.
        Right: mean decision times for the IA network with input magnitude $u = 0.2$ (solid) and $u = 1$ (dashed).
        Error bars denote bootstrapped 95\% confidence intervals.
    }\label{fig:time}
\end{figure*}

Finally, looking at the transient responses both models might produce outputs of losing choices.
For the LCA network the magnitude of the transient response mainly increases with the amount of noise (Fig.~\ref{fig:transient}a).
For the IA network, transient outputs are smaller in noisy conditions, but can be higher than for the LCA network in less noisy conditions with small target separations.
The magnitude of such transient responses is reduced by adjusting $\tau_1$ to 0.5.
\begin{figure*}
    \centering
    \includegraphics{figures/transient}
    \caption{
        Transient response (highest output of losing choices) for the LCA and IA network.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal lines show the optimum.
    }\label{fig:transient}
\end{figure*}
